Analysis

### 2021-12-05 code/R/Analysis.Rmd
Added images to gitignore and renamed scripts

>>>>

```{r}
thul01$x_c = (thul01$x_min + thul01$x_max) / 2
thul01$y_c = (thul01$y_min + thul01$y_max) / 2

thul01 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = Class)) + 
  xlim(0,6080) +
  ylim(0,3420)

nyaa04$x_c = (nyaa04$x_min + nyaa04$x_max) / 2
nyaa04$y_c = (nyaa04$y_min + nyaa04$y_max) / 2

nyaa04 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = Class), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  theme(legend.position = "none")

```{r}
tracksThul01 = read.csv('../../trackResults4.csv',stringsAsFactors = FALSE)

tracksThul01$x_c = as.numeric(tracksThul01$x_C)

tracksThul01 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(objectID))) + 
  xlim(0,6080) +
  ylim(0,3420)
```
